Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-28 draft/ms_v5.tex
Make it clear about accuracy v.s. precision

    The Subaru Strategic Program (SSP) is an ambitious wide-area, multi-band survey
    using the Hyper Suprime-Cam (HSC) on the Subaru telescope. 
    The Wide layer of the SSP is both wide and deep, reaching a detection limit of 
    $i{\sim}26.0$ mag. 
    At these depths, it is challenging to achieve accurate, unbiased, and consistent
    photometry across all five bands. 
    The HSC data are reduced using a pipeline that builds on the prototype pipeline 
    being designed by the Large Synoptic Survey Telescope’s Data Management system. 
    We have developed a \texttt{Python}-based, flexible framework to inject synthetic
    galaxies into real HSC images called \synpipe{}. 
    In this paper, we explain the design and implementation of \synpipe{} and generate 
    a sample of synthetic galaxies to examine the photometric performance of the HSC
    pipeline. 
    For stars, we achieve 1\% photometry at $i{\sim}18.0$ mag and 7\% photometry at
    $i{\sim}25.5$ in the $i$-band (corresponding to statistical accuracies of 
    ${\sim}0.01$ and ${\sim}0.06$ mag respectively).  
    For synthetic galaxies with single-\ser{} profiles, forced \cmodel{} photometry
    achieves 7\% photometry at $i{\sim}20.0$ mag and 11\% photometry at $i{\sim}25.0$ 
    in the $i$-band (corresponding to statistical accuracies of ${\sim}0.14$ and 
    ${\sim}0.20$ mag respectively). 
    We show that both \forced{} PSF and \cmodel{} photometry yield unbiased color 
    estimates that are robust to seeing conditions. 
    We identify several caveats that apply to the version of HSC pipeline used for 
    the first public HSC data release (DR1) that need to be taking into consideration. 
    First, the degree to which an object is blended with other objects impacts the 
    overall photometric performance.  
    This is especially true for point sources. 
    Highly blended objects tend to have larger photometric uncertainties, 
    systematically underestimated fluxes and slightly biased colors. 
    Second, $>20$\% of stars at $22.5< i < 25.0$ mag can be misclassified as 
    extended objects.
    Third, the current \cmodel{} algorithm tends to strongly underestimate the 
    half-light radius and ellipticities of galaxies with $i>21.5$ mag.

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Magnitude v.s S/N for stars
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_psf_sn}
    \end{center}
    \caption{
        Relation between input magnitudes (\textbf{left}: $i$-band; \textbf{right}:
        $g$-band) of synthetic stars and the $log(S/N)$ measured by \hscpipe{} PSF
        photometry.
        Hexagonal binned density plots and contours show the distributions for
        stars in both the good- and bad-seeing \tracts{}. 
        Highly blended stars are highlighted using scatter plots.
        The gray dashed line marks $S/N = 5$ which is the detection threshold used 
        by \hscpipe{}.  
        Our 5$\sigma$ point source detection limit is ${\sim}26.5$ mag in $i$-band,
        however we do not reach these magnitudes with our current synthetic stellar 
        input catalog.
        }
    \label{fig:star_sn}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    We randomly inject ${\sim}100,000$ stars into each \tract{} in all five bands. 
    Approximately ${\sim}3$--$4$\% of the stars are located within 2 pixels of the 
    centroids of real objects; we remove those stars from the sample to avoid confusion 
    in the comparisons.
    For matched stars, we select the primary detections 
    (\texttt{detect.is-primary=True}) that have good photometric quality
    (see Appendix \ref{app:qc} for details).
    This gives us ${\sim}83,000$ stars in each \tract{}.

@@

    In the following comparisons, we show the results from the
    \texttt{goodSeeing} and \texttt{badSeeing} \tracts{} separately because it
    is important to understand how the seeing condition affects photometric accuracy 
    as well as to test whether \hscpipe{} can deliver unbiased photometry under 
    different seeing conditions.

@@

    At \s2n{}$=5$, HSC Wide can detect stars as faint as ${\sim}26.5$ mag in both $g$ 
    and $i$ bands, which is consistent with the values found in \citet{HSCDR1} for 
    average seeing conditions.
    At the same time, it is worth reminding HSC data users that the detection
    limit will show spatial variations due to the seeing conditions.

%% ------------------------------------------------------------------------------------ %%
\subsubsection{Accuracy of PSF magnitudes}

    We now investigate the accuracy of the PSF magnitude in each of the five bands
    independently. 
    Fig \ref{fig:psf_mag} shows the difference between the input magnitude versus the
    \hscpipe{} \forced{} PSF magnitude as a function of input magnitude.

>>>>

    The Subaru Strategic Program (SSP) is an ambitious wide-area, multi-band survey
    using the Hyper Suprime-Cam (HSC) on the Subaru telescope. 
    The Wide layer of the SSP is both wide and deep, reaching a detection limit of 
    $i{\sim}26.0$ mag. 
    At these depths, it is challenging to achieve accurate, unbiased, and consistent
    photometry across all five bands. 
    The HSC data are reduced using a pipeline that builds on the prototype pipeline 
    being designed by the Large Synoptic Survey Telescope’s Data Management system. 
    We have developed a \texttt{Python}-based, flexible framework to inject synthetic
    galaxies into real HSC images called \synpipe{}. 
    In this paper, we explain the design and implementation of \synpipe{} and generate 
    a sample of synthetic galaxies to examine the photometric performance of the HSC
    pipeline. 
    For stars, we achieve 1\% photometric precision at $i{\sim}18.0$ mag and 7\%
    precision at $i{\sim}25.5$ in the $i$-band (corresponding to statistical scatters 
    of ${\sim}0.01$ and ${\sim}0.06$ mag respectively).  
    For synthetic galaxies with single-\ser{} profiles, forced \cmodel{} photometry
    achieves 7\% photometric precision at $i{\sim}20.0$ mag and 11\% precision at 
    $i{\sim}25.0$ in the $i$-band (corresponding to statistical scatters of 
    ${\sim}0.14$ and ${\sim}0.20$ mag respectively). 
    We show that both \forced{} PSF and \cmodel{} photometry yield unbiased color 
    estimates that are robust to seeing conditions. 
    We identify several caveats that apply to the version of HSC pipeline used for 
    the first public HSC data release (DR1) that need to be taking into consideration. 
    First, the degree to which an object is blended with other objects impacts the 
    overall photometric performance.  
    This is especially true for point sources. 
    Highly blended objects tend to have larger photometric uncertainties, 
    systematically underestimated fluxes and slightly biased colors. 
    Second, $>20$\% of stars at $22.5< i < 25.0$ mag can be misclassified as 
    extended objects.
    Third, the current \cmodel{} algorithm tends to strongly underestimate the 
    half-light radius and ellipticities of galaxies with $i>21.5$ mag.

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Magnitude v.s S/N for stars
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_psf_sn}
    \end{center}
    \caption{
        Relation between input magnitudes (\textbf{left}: $i$-band; \textbf{right}:
        $g$-band) of synthetic stars and the $\log (S/N)$ measured by \hscpipe{} PSF
        photometry.
        Hexagonal binned density plots and contours show the distributions for
        stars in both the good- and bad-seeing \tracts{}. 
        Highly blended stars are highlighted using scatter plots.
        The gray dashed line marks $S/N = 5$ which is the detection threshold used 
        by \hscpipe{}.  
        Our 5$\sigma$ point source detection limit is ${\sim}26.5$ mag in $i$-band,
        however we do not reach these magnitudes with our current synthetic stellar 
        input catalog.
        }
    \label{fig:star_sn}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    We randomly inject ${\sim}100,000$ stars into each \tract{} in all five bands. 
    Typically, there are ${\sim}80000$ stars with $i_{\mathrm{PSF}}<26.0$ in one HSC 
    \tract{}. 
    Approximately ${\sim}3$--$4$\% of the stars are located within 2 pixels of the 
    centroids of real objects; we remove those stars from the sample to avoid confusion 
    in the comparisons.
    For matched stars, we select the primary detections 
    (\texttt{detect.is-primary=True}) that have good photometric quality
    (see Appendix \ref{app:qc} for details).
    This gives us ${\sim}83,000$ stars in each \tract{}.

@@

    In the following comparisons, we show the results from the
    \texttt{goodSeeing} and \texttt{badSeeing} \tracts{} separately because it
    is important to understand how the seeing conditions affects photometric accuracy 
    as well as to test whether \hscpipe{} can deliver unbiased photometry under 
    different seeing conditions.

@@

    At \s2n{}$=5$, HSC Wide can detect stars as faint as ${\sim}26.5$ mag in both $g$ 
    and $i$ bands, which is consistent with the values found in \citet{HSCDR1} for 
    average seeing conditions.
    However, it is worth reminding HSC data users that the detection
    limit will exhibit spatial variations due to the seeing conditions.

%% ------------------------------------------------------------------------------------ %%
\subsubsection{Precision and Accuracy of PSF magnitudes}

    We now investigate the performance of the PSF photometry in each of the five bands
    independently. 
    Fig \ref{fig:psf_mag} shows the difference between the input magnitude versus the
    \hscpipe{} \forced{} PSF magnitude ($\Delta \mathrm{mag}_{\mathrm{PSF}}$) as a 
    function of input magnitude. 
    We separate these stars into seven input magnitude bins.  
    In each bin, we characterize the \textbf{precision} of the PSF magnitude using 
    the standard deviation of the $\Delta \mathrm{mag}_{\mathrm{PSF}}$ distribution.
    Meanwhile, we characterize the \textbf{accuracy} of the PSF magnitude via the 
    mean magnitude difference in each bin. 
    This also informs us whether the PSF photometry is biased at certain input 
    magnitude.
